Thermodynamic fragments in magic state theories

### 2020-11-25 magic_paper.tex
tidying up

Monotones are often used \nick{CITE} to address the question of state convertibility, although such approaches are usually generic.
A monotone of any general resource theory is a projection of the theory onto the non-negative real numbers, collapsing the pre-order of the theory to the total order defined on the real line.
This is the \nick{most naive} non-trivial projection under which the images of incomparable states can be compared.
Our first contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure.
Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
We show that a magic theory can be subdivided into \emph{fragments} \nick{expand}

@@

The Wigner distributions of different types of qutrit states are illustrated in~\cref{fig:wstate_examples}.
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:maxmix}%
    \includegraphics[height=2cm]{figs/maxmixed.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:zero}%
    \includegraphics[height=2cm]{figs/zerostate.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:bound}%
    \includegraphics[height=2cm]{figs/boundstate.pdf}
    %\caption{Bound state}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:strange}%
    \includegraphics[height=2cm]{figs/strangestate.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$ \nick{CITE}.
    \nick{Explain what a magic / bound magic state is in intro}
    }%
    \label{fig:wstate_examples}
\end{figure}

@@

\begin{theorem}\label{thm:sigmamajor}
    Let $\R = (\F, \O)$ be a theory of magic. Then $\rho \longrightarrow \tau$ is possible iff  $\W{\tau} \prec_\sigma \W{\rho}$ within a $\sigma$--fragment.
    \nick{I understand that dropping the full-rank assumption on $\sigma$ makes the statement a lot stronger, but also incorrect e.g. in the case of the replacement channel $\E(\rho) = \ketbra{0}$, since $d$-majorization in $\O_{\ketbra{0}}$ is not well-defined.}
\end{theorem}
\begin{proof}
Suppose we can convert $\rho$ into $\tau$ in the magic theory. 
Thus there is some $\O_\sigma$ and some $\E \in \O_\sigma$ such that $\E(\rho) = \tau$, and $\E(\sigma)=\sigma$. 
Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$. 
Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
\end{proof}
This result can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
However the majorization constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- this enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.

@@

    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$, where
    \begin{equation}\label{eq:lorenz}
        (x_k, \lc{\bmz}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right) \in \mathbb{R}^2.
    \end{equation}
    We define the set of points on this curve, $\lc{\bmz}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmz$ with respect to $\bmd$.
\end{definition}
Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\tilde{\bmz}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.

@@

\section{Magic state interconversion and Lorenz curves}
\label{sec:distill}

@@

\subsection{Mana and majorization in magic theories}\label{sec:scmana}
We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them proceeds. 
Mana is the fundamental resource monotone for magic. 
Here we show that its properties are in fact special cases of more general majorization features. 
More precisely, its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.

@@

Consider a general magic state interconversion in $\O_\sigma$, $\rho \xrightarrow{\E \in \O_\sigma} \tau$.
It is shown in~\cref{app:major} that mana is an additive monotone in every $\sigma$--fragment under $d$--majorization, so it provides a necessary condition for the process to be possible,
\begin{equation}\label{eq:manabound}
    \mana{\rho} \geq \mana{\tau}. %{\rm{C}}_{\rm{mana}}(\rho, \tau, \sigma):\ 
\end{equation}
A new bound can be obtained in the $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
\begin{equation}\label{eq:majbound}
    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1].
\end{equation}
If one of these consitions is not satisfied, then the Lorenz curve of initial state $\rho$ is below the curve of target $\tau$ at some point $x$ and the conversion is not possible.

In fact, our current setting makes it apparent that the mana condition is always weaker than the majorization condition for all magic state interconversions.

We first show that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ discussed in~\cref{sec:mono}
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	For notational simplicity, denote $(\W{\rho})_i = \W[\bmx]{\rho},\ i = 1,\dots, d^2$ and similarly for $\W{\sigma}$.
	We choose the index mapping so that the vector of component ratios, 
	\begin{equation}
		\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\rho})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{d^2}}{(\W{\sigma})_{d^2}} \right)^T,
	\end{equation}
	is sorted in the sense that $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
	Note that all components of $\W{\sigma}$ are positive, so $(\tilde{\bm{w}})_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.

	Let $k_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
	Then, $(\W{\rho})_i < 0$ if and only if $i > k_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
	\begin{equation}
		\lc{\rho}{\sigma}(x_{k_\star}) = \sum_{i=1}^{k_\star} (\W{\rho})_i,
	\end{equation}
	and is achieved at
	\begin{equation}\label{eq:maxloc}
		x_{k_\star} \coloneqq \sum_{i=1}^{k_\star} (\W{\sigma})_i.
	\end{equation}

@@

We can therefore view mana as just one of the features of the Lorenz curve, namely its maximum value. This implies the following result.
\begin{theorem}\label{thm:bounds}
    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in every $\sigma$--fragment.
\end{theorem}
\begin{proof}
    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
    \begin{equation}
        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
    \end{equation}
    Therefore, the $\W{\sigma}$--majorization bound
    \begin{equation}
    	\lc{\rho}{\sigma}(x) \geq \lc{\rho}{\sigma}(x),\ x\in[0,1]
    \end{equation}
    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.
\end{proof}

Of practical importance are magic state distillation (MSD) processes of the form
\begin{equation}\label{eq:distprocess}
    \rho^{\otimes n} \xrightarrow{\E \in \O_\sigma} \tau,
\end{equation}
where $n$ copies of a noisy magic state $\rho$ are converted into a target single-copy state $\tau$. \nick{expand?}

In general, the Wigner components of a $n$-copy state $\rho^{\otimes n}$ can be calculated directly from $W_\rho$, along with their multiplicities, by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$. \nick{is this clear?}
This follows from the multiplicativity of the Wigner distribution.

As an example, consider the qutrit Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
It is the simplest non-trivial case to analyse because its Wigner distribution consists of two distinct components.
Calculating the components of $\ket{S}\bra{S}^{\otimes n}$ allows for analytical calculation of the maximum of the $n$-copy state,
\begin{equation}\label{eq:Skmax}
    \max_x{\lc{\ketbra{S}^{\otimes n}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^n \right).
\end{equation}
Its location $x_{k_\star}$ depends on the $\sigma$--fragment and is given by~\cref{eq:maxloc} with $k_\star = \frac{1}{2}(7^n + 9^n)$.
%1 + \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{\floor{\frac{n-1}{2}}} 4^{-(2j+1)} \binom{n}{2j+1}
%\sum_{i=j, j: odd}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n - (1-a)^n ]
%$\{(-1)^j 2^{j-n} 3^{-n}\}_{0 \leq j \leq n}$ with multiplicity $8^{n-j} \binom{n}{j}$ for the $j$-th term

Consider the problem of purifying out magic from a noisy Strange state,
\begin{equation}
    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
\end{equation}
in $\O_\sigma$.
At noise levels $\epsilon \geq \frac{3}{4}$, the state is sufficiently noisy so as the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ no longer contains negativities. 
At any $\epsilon \leq \frac{3}{4}$, we can investigate the distillation process resulting in a single-copy state with sufficiently low target $\epsilon_{\tau}$,
\begin{equation}\label{eq:sdist}
	\noisysn \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
\end{equation}

The more noisy the initial state is, the more copies needed to reach the target, therefore it makes sense to define a noise level threshold 
\begin{equation}\label{eq:ethresh}
	\epsilon_{\rm{th}}(n, \epsilon_\tau, \sigma) \coloneqq \sup{\{\epsilon:\ \lc{\noisysn}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}},
\end{equation}
so that the MSD process~(\ref{eq:sdist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(n, \epsilon_\tau, \sigma)$

\nick{Condition in~\cref{eq:ethresh} is informally written. Can also define 
\begin{equation}\label{eq:ethresh}
	n_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{n:\ n \in \mathbb{N}, \lc{\noisysn}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
\end{equation}}
We now examine the MSD process~(\ref{eq:sdist}) in specific $\sigma$--fragments.

\subsection{Magic in unital fragments}\label{sec:unital}

@@

If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}

We plot the Lorenz curves of pure and noisy Strange state $n$-copy states for $n$ up to $4$ in~\cref{fig:lcs}.
For $n=1$, the Lorenz curve is simply additive, 
\begin{equation}
\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
\end{equation}
for any $\sigma, \rho$, but for $n\geq 2$, calculations become more complicated.

>>>>

Monotones are often used \nick{CITE} to address the question of state convertibility, although such approaches are usually generic.
We highlight the defining property of a monotone here, as it is useful in several sections that follow.
\begin{definition}[\textbf{Resource monotone}]\label{def:mono}
    Let $\R = (\F, \O)$ be a resource theory.
    A resource monotone $\M$ is a projection from the set of quantum states of the theory onto the real line, so that $\M$ is monotonically decreasing under free operations,
    \begin{equation}
        \M(\rho_1) \leq \M(\rho_2)\ \text{whenever}\ \rho_1 \prec_{\R} \rho_2.
    \end{equation}
\end{definition}
The monotonicity condition reflects the no resource generating property of free operations, so that monotones respect the pre-order $\prec_\R$ of the theory.
A monotone of any general resource theory is a projection of the theory onto the non-negative real numbers, collapsing the pre-order of the theory to the total order defined on the real line.
Our contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure (as opposed to the real line).
Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
We show that a magic theory can be subdivided into \emph{fragments} \nick{expand}

@@

The Wigner distributions of different types of qutrit states are illustrated in~\cref{fig:wstate_examples}.
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:maxmix}%
    \includegraphics[height=2cm]{figs/maxmixed.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:zero}%
    \includegraphics[height=2cm]{figs/zerostate.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:bound}%
    \includegraphics[height=2cm]{figs/boundstate.pdf}
    %\caption{Bound state}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:strange}%
    \includegraphics[height=2cm]{figs/strangestate.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$ \nick{CITE}.
    \nick{Explain what a magic state is in intro}
    }%
    \label{fig:wstate_examples}
\end{figure}

@@

\begin{theorem}\label{thm:sigmamajor}
    Let $\R = (\F, \O)$ be a theory of magic. Then $\rho \longrightarrow \tau$ is possible \nick{only if}  $\W{\tau} \prec_\sigma \W{\rho}$ within a $\sigma$--fragment.
\end{theorem}
\begin{proof}
Suppose we can convert $\rho$ into $\tau$ in the magic theory. 
Thus there is some $\O_\sigma$ and some $\E \in \O_\sigma$ such that $\E(\rho) = \tau$, and $\E(\sigma)=\sigma$. 
Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$. 
Since $\sigma$ is \nick{full-rank} and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
\end{proof}
This result can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
However the majorization constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- this enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.

@@

    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$, where
    \begin{equation}\label{eq:lorenz}
        (x_k, \lc{\bmz}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right) \in \mathbb{R}^2.
    \end{equation}
    We define the set of points on this curve, $\lc{\bmz}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmz$ with respect to $\bmd$.
\end{definition}
Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\tilde{\bmz}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
Finally, points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.

@@

\section{Magic state interconversion and Lorenz curve comparison}
\label{sec:distill}

@@

\subsection{Majorization in magic theories}\label{sec:scmana}
We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them proceeds.

@@

Consider a general magic state interconversion in $\O_\sigma$, 
\begin{equation}
	\rho \xrightarrow{\E \in \O_\sigma} \tau.
\end{equation}

Magic theories utilise monotone bounds of the form
\begin{equation}\label{eq:majbound}
    \M(\rho) \geq \M(\tau),
\end{equation}
to determine whether the interconversion is allowed.
Monotone bounds hold independently of $\sigma$--fragments, therefore they provide no understanding with regard to the type of operations that allow the interconversion.

New bounds can be obtained in the $\sigma$--fragment by pointwise Lorenz curve comparison of the initial and target states,
\begin{equation}\label{eq:majbound}
    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1].
\end{equation}
This inequality is parametrised by $x$ and if it is not satisfied at any point $x$, then the Lorenz curves intersect and the conversion is impossible.

We can reduce the number of independent constraints stemming from this inequality down to the number of elbows of the target state.
\begin{theorem}\label{thm:elbows}
	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.

	Let $r$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_\kk\}$ be their locations.

	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,\kk$.
\end{theorem}
\begin{proof}	
	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,\kk$.

	Conversely, assume that $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.
	First, let $x_0 = 0$ and $x_{\kk+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{\kk+1}) = \lc{\tau}{\sigma}(x_{\kk+1}) = 1$.
	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{\kk+1}\}$.

	Pick two consecutive locations $x_i, x_{i+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_i, \lc{\tau}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_i, \lc{\rho}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
	This is illustrated in~\cref{fig:elbows_proof}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{figs/elbows_proof.pdf}
    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
    }
    \label{fig:elbows_proof}
\end{figure}

	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_i, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,\kk$, so the proof is complete.
\end{proof}
This theorem is of practical importance in checking Lorenz curve bounds, and it is used in the discussion of standard Lorenz curves in~\cref{sec:lcsu}.

\nick{We can skip mana and just discuss sum-negativity}

One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{(2\sn{\rho}+1)},
\end{equation}
where the \emph{sum-negativity} ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}
Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical is distillation settings.} magic monotone, so it provides a necessary condition for magic state interconvertibility.

Here, we show that its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
In fact, our current setting makes it apparent that the mana provides a weaker condition than majorization for all magic state interconversions.

We first show that the Lorenz curve maximum of state $\rho$ is independent of the $\sigma$--fragment and directly related to its sum-negativity.
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	For notational simplicity, denote $(\W{\rho})_i = \W[\bmx]{\rho},\ i = 1,\dots, d^2$ and similarly for $\W{\sigma}$.
	We choose the index mapping so that the vector of component ratios, 
	\begin{equation}
		\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\rho})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{d^2}}{(\W{\sigma})_{d^2}} \right)^T,
	\end{equation}
	is sorted in the sense that $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
	Note that all components of $\W{\sigma}$ are positive, so $(\tilde{\bm{w}})_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.

	Let $\jj_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
	Then, $(\W{\rho})_i < 0$ if and only if $i > \jj_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
	\begin{equation}
		\lc{\rho}{\sigma}(x_{\jj_\star}) = \sum_{i=1}^{\jj_\star} (\W{\rho})_i,
	\end{equation}
	and is achieved at
	\begin{equation}\label{eq:maxloc}
		x_{\jj_\star} \coloneqq \sum_{i=1}^{\jj_\star} (\W{\sigma})_i.
	\end{equation}

@@

We can therefore view mana as just one feature of the Lorenz curve, namely its maximum value. 
This implies the following result.
\begin{theorem}\label{thm:bounds}
    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in every $\sigma$--fragment.
\end{theorem}
\begin{proof}
    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
    \begin{equation}
        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
    \end{equation}
    Therefore, the majorization bound
    \begin{equation}
    	\lc{\rho}{\sigma}(x) \geq \lc{\rho}{\sigma}(x),\ x\in[0,1]
    \end{equation}
    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.
\end{proof}

Denote an $n$-copy, $\epsilon$-noisy magic state $\rho$ in the $\sigma$--fragment by
\begin{equation}\label{eq:dist}
    \rho(\epsilon)\too{\nn} = \left[ (1 - \epsilon) \rho + \epsilon \sigma \right]\too{\nn},
\end{equation}
and consider the general magic state distillation (MSD) / purification process
\begin{equation}
		\rho(\epsilon)\too{\nn} \xrightarrow{\E \in \O_\sigma} \rho(\epsilon')\too{\kk},
\end{equation}
where it is converted into a $\kk$-copy, $\epsilon'$-noisy state, such that the number of copies has decreased ($\kk < \nn$), but the state is less noisy ($\epsilon' < \epsilon$).

The more noisy the initial state is, the more copies needed to reach the target. 
We make this idea precise by defining the \emph{noise level threshold} as
\begin{equation}\label{eq:ethresh}
	\begin{split}
	\epsilon_{\rm{th}}(\nn, \kk, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{\nn}}{\sigma}}(x) \geq \\
	&{\lc{\rho(\epsilon')\too{\kk}}{\sigma}(x),\ x\in[0,1]\}}.
	\end{split}
\end{equation}
The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(\nn, \kk, \epsilon', \sigma)$.

\nick{Can also define a distillation bound
\begin{equation}\label{eq:ethresh}
	\nn_{\rm{th}}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{\nn:\ \nn \in \mathbb{N}, \lc{\noisysn}{\sigma} \geq \lc{\noisys(\epsilon')}{\sigma}\}}.
\end{equation}}

In general, the Wigner components of an $n$-copy state $\rho\too{n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
\begin{equation}
	\W{\rho\too{\NN}} = \rm{W}_{\rho}\too{\NN},
\end{equation}
where $\otimes$ can be interpreted as the usual Kroenecker product in the last expression.
Furthermore, single-copy Lorenz curves are simply additive in noise, 
\begin{equation}
\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
\end{equation}
for any $\sigma, \rho$.
This is not true for higher number of copies.

An important example is the purificiation process~\cref{eq:dist} of the qutrit Strange state $\ketbra{\rm{S}}$,
\begin{equation}
    \noisys(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
\end{equation}
in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange}. 
For $\epsilon=0$, this state is a qutrit of maximal sum-negativity \nick{CITE} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.

In~\cref{fig:lcs}, we illustrate the Lorenz curves of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$-fragments.
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:lcs_maxmix}%
    \includegraphics[height=3cm]{figs/lcs_maxmix.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_thermal}%
    \includegraphics[height=3cm]{figs/lcs_thermal.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:lcs_zero}%
    \includegraphics[height=3cm]{figs/lcs_zero.pdf}
    %\caption{Bound state}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_one}%
    \includegraphics[height=3cm]{figs/lcs_one.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\noisysn$ for $n=1,2,3,4$.
    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
    \subref{fig:lcs_maxmix} Unital fragment; \subref{fig:lcs_thermal} Thermal fragment with $H = (0,1,2)$ and $\beta = 0.5$; \subref{fig:lcs_zero} Fragment $\O_{\ketbra{0}{0}}$ (corresponds to red curve in~\cref{fig:stab_distill}); \subref{fig:lcs_one} Fragment $\O_{\ketbra{1}{1}}$ (corresponds to blue curve in~\cref{fig:stab_distill}). 
    }%
    \label{fig:lcs}
\end{figure}

In the following sections, we address the question of state interconversions in various $\sigma$--fragments, including concrete examples of the Strange state distillation process. \nick{adapt}

\subsection{Magic in the unital fragment}\label{sec:unital}

@@

If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}
\begin{figure}[b]
    \centering
    \includegraphics[scale=0.5]{figs/unital_distill.pdf}
    \caption{\textbf{Noise thresholds in unital fragment.} Mana and Lorenz curve noise thresholds for the Strange state purification process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
    Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
    The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities.
    }
    \label{fig:unital_distill}
\end{figure}

\iffalse
% Copies plot
\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/unital_distill_copies.pdf}
    \caption{\textbf{Copies required for Strange state distillation.} Mana and Lorenz curve copy thresholds for the Strange state purification process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
    Lorenz curve comparison consistently provides higher low bounds on the number of noisy Strange state copies required.
    }
    \label{fig:unital_distill_copies}
\end{figure}
\fi

In~\cref{fig:unital_distill}, we examine the Strange state distillation process of~\cref{eq:dist} with $\epsilon' = 0.05$ which describes all circuits that respect the unital symmetry.
Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
\nick{Explain asymptotic behaviour?}

\nick{We devote a section on Strange state Lorenz curve analysis in the unital fragment}

\null\newpage

\subsection{Strange state interconversions in the unital fragment}\label{sec:lcsu}

In this section we analytically investigate the behaviour of the Lorenz curve of an $n$-copy Strange state in the unital fragment ($\sigma = \id/3$), 
\begin{equation}\label{eq:lcsu}
	\lc{\noisysn}{\frac{1}{d}\id}(x),\ x\in[0,1].
\end{equation}
We recognise Lorenz curve of this type as ``standard candles'' in the context of magic state distillation and call them the \emph{standard Lorenz curves} \nick{expand}.

The aim is to study the MSD process,
\begin{equation}\label{eq:sudist}
	\noisysn \xrightarrow{\E \in \O_{\id/3}} \noisys(\epsilon')\too{\kk},
\end{equation}
in the regime where $0 \leq \epsilon \leq \tfrac{3}{4}$.
For $\tfrac{3}{4} \leq \epsilon < 1$, the noisy Strange state $\noisys(\epsilon)$ contains no Wigner negativities in the unital fragment as seen in~\cref{eq:wsu}.
